Exploring Hillary Clinton's Emails\thanks{STATS 601 final project.}

### 2016-04-19 paper/paper.tex
add figures to paper

@@

@@

\begin{figure}[htb] \centering
  \includegraphics[width=0.95\linewidth]{../images/coefficients.pdf}
  \caption{Normalized coefficients from a multinomial logistic regression of email sender on LDA topic proportions.}
  \label{fig:coefficients}
\end{figure}

>>>>

\begin{table}[h]
\centering
\label{topic_top_words}
\scalebox{0.8}{
\begin{tabular}{cccccc}
\toprule
Israel & Elections & Libya & Afghanistan & Int. Dev. & Obama \\
\midrule
israel & democrat & libya & afghanistan & develop & presid \\
isra & republican & secur & pakistan & state & obama \\
peace & american & travel & afghan & support & said \\
palestinian & polit & libyan & militari & global & hous \\
netanyahu & parti & iraq & general & program & white \\
east & elect & embassi & karzai & effort & administr \\
negoti & obama & attack & offici & intern & polici \\
arab & percent & kill & war & work & aid \\
state & candid & march & forc & includ & advis \\
\bottomrule
\end{tabular}
}
\caption{Some interesting content topics}
\label{tab:content_topics}
\end{table}

\begin{figure}[h]
\centering
\begin{subfigure}[Israel]{.30\linewidth}
    \includegraphics[width=\linewidth]{../images/time_plot6.pdf}
    \caption{Israel} \label{fig:t1}
\end{subfigure}
\begin{subfigure}[Election]{.30\linewidth}
    \includegraphics[width=\linewidth]{../images/time_plot11.pdf}
    \caption{Election} \label{fig:t2}
\end{subfigure}
\begin{subfigure}[Libya]{.30\linewidth}
    \includegraphics[width=\linewidth]{../images/time_plot18.pdf}
    \caption{Libya} \label{fig:t3}
\end{subfigure}
\begin{subfigure}[Afghanistan]{.30\linewidth}
    \includegraphics[width=\linewidth]{../images/time_plot27.pdf}
    \caption{Afghanistan} \label{fig:t4}
\end{subfigure}
\begin{subfigure}[Int. Dev.]{.30\linewidth}
    \includegraphics[width=\linewidth]{../images/time_plot23.pdf}
    \caption{Int. Dev.} \label{fig:t5}
\end{subfigure}
\begin{subfigure}[Obama]{.30\linewidth}
    \includegraphics[width=\linewidth]{../images/time_plot25.pdf}
    \caption{Obama} \label{fig:t6}
\end{subfigure}
\label{fig:topic_time_plots}
\end{figure}

@@

\begin{table}[h]
\centering
\label{topic_sources}
\scalebox{0.70}{
\begin{tabular}{cccccc}
\toprule
Israel & Elections & Libya & Afghanistan & Int. Dev. & Obama \\
\midrule
Sidney Blumenthal & SB & Huma Abedin & Judith McHale & JM & SB \\
(SB) & & (HA) & (JM) & & \\
\noalign{\vskip 5mm}
HA & Philippe Reines & Wendy Sherman & HA & Melanne Verveer & PR \\
& (PR) & (WS) & & (MV) & \\
\noalign{\vskip 5mm}
Jake Sullivan & JM & JS & MV & Anne-Marie & Cherly Mills \\
(JS) & & & & Slaughter (AMS) & (CM)\\
\noalign{\vskip 5mm}
AMS & CM & Monica Hanley & JS & CM & HA \\
& & (MH) & & & \\
\noalign{\vskip 5mm}
Hillary Clinton & HA & SB & Richard Verma & JS & HC \\
(HC) & & & (RV) & & \\
\bottomrule
\end{tabular}
}
\caption{Primary sources for interesting topics}
\label{tab:top_sources}
\end{table}

@@

\begin{figure}[htb] \centering
  \includegraphics[width=0.95\linewidth]{../images/coefficients.pdf}
  \caption{Standardized coefficients from a multinomial logistic regression of email sender on LDA topic proportions.}
  \label{fig:coefficients}
\end{figure}
